---
name: Limeng (Momo) Xie 
date: "`r format(Sys.time(), '%B, %Y')`"
address: 108 College Station Rd, Apt H204, Athens, GA, USA
phone: +1 443-691-8965
email: momosan@uga.edu
github: tomatopepper
linkedin: limeng-momo-xie-a15a79a6
twitter: happy_momosan
output: 
  vitae::awesomecv:
  keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# Education
```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "Phd student in Plant Biology, GPA 3.96", "University of Georgia (UGA)", "Athens, GA", "Aug 2018 - Present", "Advisor: Dr. Alexander Bucksch, Computational Plant Science Lab",
  "Master in Horticultural Science, GPA 3.81", "Texas A&M University (TAMU)", "College Station, TX", "Aug 2014 - Dec 2016", "Certificate in Applied Statistics",
   "Master in Horticultural Science, GPA 3.81", "Texas A&M University (TAMU)", "College Station, TX", "Aug 2014 - Dec 2016", "Thesis: SNP Discovery and Mapping QTLs Associated with Root Traits and Morphological Traits in Tomato",
  "Bachelor in Agronomy, GPA 3.65", "China Agricultural University (CAU)", "Beijing, China", "Sept 2009 - May 2014", "Thesis: Evaluation of Methane Production in Anaerobic Reactor with Sweet Potato Vine and Dairy Manure",
  "Exchange Student", "Saga University", "Kyushu, Japan", "Oct 2011 - Aug 2012", "Major in Plant Science and Japanese"
) %>%
  detailed_entries(degree, dates, uni, loc, details)
```
# Publications

**Xie, L.**,Burridge,J., Lynch, J.P., Bucksch, A. Phenotypic spectrum: uncovering root architecture diversity in common bean (*Phaseolus vulgaris L.*) *In prep*  

Delory, B.M., Hernandez-Soriano, M.C., Wacker, T.S., Dimitrova, A., Ding, Y., Greeley, L.A., Ng, J.L.P., Mesa-Marín, J., **Xie, L.**, Zheng, C. & York, L.M. (2022). A snapshot of the root phenotyping landscape in 2021. *bioRxiv*.

Carley, C. N., Chen, G., Das, K. K., Delory, B. M., Dimitrova, A., Ding, Y., ..., **Xie, L.** & Zheng, C. (2022). Root biology never sleeps. *New Phytologist*, 235(6), 2149-2154.

**Xie, L.**, Klein, P., Crosby, K., & Jifon, J. (2019). A genotyping-by-sequencing single nucleotide polymorphism–based map and genetic analysis of root traits in an interspecific tomato population. *Journal of the American Society for Horticultural Science*, 144(6), 394-404.

# Presentations

2022 **Xie, L.**, Burridge,J., Lynch, J.P., Kengkanna, J., Wallace, J., Hanlon, M., Bucksch, A., **ASA, CSSA, SSSA International Annual Meeting**, _Phenotypic Spectrum: A Novel Framework to Study the Root Architecture Diversity of Crop Roots at the Population Level_, Baltimore, MD 

2022 **Xie, L.**, Burridge,J., Lynch, J.P., Bucksch, A., **Bayer Crop Sciences**, _Phenotypic Spectrum: A Novel Framework to Study the Root Architecture Diversity of Common Bean_, Chesterfield, MO 

2022 **Xie, L.**, Burridge,J., Lynch, J.P., Bucksch, A., **North America Plant Phenoytping Network Annual Meeting**, _Phenotypic Spectrum: Uncovering Root Architecture Diversity in Common Bean (Phaseolus vulgaris .L)_ Athens, GA

2021 **Xie, L.**, Burridge,J., Lynch, J.P., Bucksch, A., **ASA, CSSA, SSSA International Annual Meeting**, _Phenotypic Spectrum: Uncovering Root Architecture Diversity in Common Bean (Phaseolus vulgaris .L)_, (Poster), Salt Lake City, UT

2020 **Xie, L.**,Burridge,J., Klepp, N., Miller, J.,Lynch, J.P., Bucksch, A., **the 7th International Horticulture Research Conference**,  _Quantifying diversity of root architecture types within a genotype of common bean (Phaseolus vulgaris .L)_, Online

2019 **Xie, L.**, Bucksch, A., **International Plant Phenotyping Symposium**, _The shape of plants revealed: A shape theoretic perspective on statistics of trait measurements_, Nanjing, China

2019 **Xie, L.**,Burridge,J., Klepp, N., Miller, J., Chutoe, C., Saengwilai, P., Lynch, J.P., Bucksch, A., **Crops Conference**, _The Phenotypic Spectrum: Identifying Whole Role Architecture Types in Genotypes of Common Bean (_Phaseolus vulgaris, L) (Poster)_, Huntsville, AL 

2018 **Xie, L.**, Liu, S, Bucksch., A., **Plant Center Fall Retreat**,  _Extracting Traits from 3D Models of Maize Root System Architecture (Poster)_, Unicoi State Park, GA  

2017 **Xie, L.**, Klein, P., Crosby, K., & Jifon, J., **American Society of Horticultural Science Annual Meeting**, _Mapping Novel QTLs Associated with Root Morphological Traits in an Interspecific Tomato Population_, Waikoloa, HI  

2015 **Xie, L.**, Crosby, K., & Jifon, J., **American Society of Horticultural Science Annual Meeting**, _Estimates of Genetic Variance for Drought Tolerance Traits in Tomato (Poster)_, New Orleans, LA 


# Honors and Awards
2022 Travel Grant, Graduate School, UGA    
2022 Palfrey Travel Award, Department of Plant Biology, UGA  
2022 Georgia Education Board Fellowship, UGA       
2022 Gerald O Mott Award, Crop Science Society of America    
2022 Best Fast-Forward Talk at North America Plant Phenotyping Network Annual Meeting    
2021 1st place UGA Plant Phenotyping and Robotics Symposium Poster Competition    
2021 Georgia Education Board Fellowship, UGA  
2020 Palfrey Travel Award, Department of Plant Biology, UGA      
2020 Travel Scholarship for Root Short Course, University of Florida     
2016 Outstanding Graduate Student Award, Texas Plant Protection Association  
2013 Third Prize Scholarship for Academic Excellence, CAU  
2012 Japan Student Service Scholarship, Japan Student Service Organization  
2011 Third Prize Scholarship for Academic Excellence, CAU  
2010 Second Prize Scholarship for Academic Excellence, CAU  
2010 National Encouragement Scholarship, Ministry of Education in China  
2010 Merit Undergraduate Student Award, CAU 

# Leadership Activities

2022 Selected into competitive Emerging Leaders Program (UGA) for leadership training    
2022 Organized root phenotyping workshop for UGA Institute Of Plant Breeding, Genetics, And Genomics graduate students    
2021 Ambassador of International Society of Root Research |Promoted and advocated root research at the social media platform | Published meeting report in the academic journal     
2021 Panelist Speaker of Women in STEM for Outreach Activities in Athens‐Clarke County High School  
2021 Judge for Senior Section of 73rd Georgia Science & Engineering Fair  
2020 Judge Lead for Junior Section of 72nd Georgia Science & Engineering Fair  
2019 Judge for Senior Section of 71st Georgia Science & Engineering Fair  
2019 Executive Board Member of Chinese Genomics Online Meet‐up | Responsible for inviting guest speakers and technical support for live stream  
2018 Volunteer in March for Science at Washington, DC   
2017 Organized tomato field day for farmers in Brazos County, Texas   
2015 Secretary, Texas A&M Horticulture Graduate Student Council  

# Research Experience 

```{r research}
tribble(
  ~ positon, ~ uni, ~ loc, ~ dates, ~ details,
  "Graduate Reserch Assistant", "Computational Plant Science Lab, UGA", "Athens, GA", "Jan 2019 - Present", " Developed a computing pipeline to quantify the root architecture diversity of crop roots (common bean and maize) at the population level",
  "Graduate Reserch Assistant", "Computational Plant Science Lab, UGA", "Athens, GA", "Jan 2019 - Present", "Established an Indoor-Field: A macro-mesocosm system to study the field dynamics of phenotypic spectrum of common bean",
  "North America Breeding Intern", "Bayer Crop Science", "Chesterfield, MO", "May 2022  - Aug 2022", "Developed a root phenotyping platform for cotton breeding program",
  "North America Breeding Intern", "Bayer Crop Science", "Chesterfield, MO", "May 2022  - Aug 2022", "Identified root traits that improve cotton performance in drought from control enviroment to field scale",
  "North America Breeding Intern", "Bayer Crop Science", "Chesterfield, MO", "May 2022  - Aug 2022", "Presented findings to stakeholders across teams",
  "Graduate Reserch Assistant", "Integrated Plant Science Program, UGA", "Athens, GA", "Aug 2018  - Dec 2018", "Developed an image processing pipeline to automatically extract root traits from 3D models of maize root system (Rotation project at Bucksch Lab)",
   "Graduate Reserch Assistant", "Integrated Plant Science Program, UGA", "Athens, GA", "Aug 2018  - Dec 2018", "Identified potential genetic regions with insulators in Bladderwort by analyzing a public RNA-seq database (Rotation project at Wallace Lab)",
  "Graduate Reserch Assistant", "Integrated Plant Science Program, UGA", "Athens, GA", "Aug 2018  - Dec 2018", "Explored genetic variation of volatile content among 150 tomato accessions (Rotation project at van der Knaap Lab)",
  "Lab Techician", "Vegetable Breeding Lab, TAMU", "College Station, TX", "May 2017 - Dec 2017", "Conducted all daily operations including plant, fertilize, trellis, prune, IPM, supplies and asset acquisition to complete short term and long breeding  goals over 7 greenhouses and acre-size field",
  "Lab Techician", "Vegetable Breeding Lab, TAMU", "College Station, TX", "May 2017 - Dec 2017", "Established greenhouse trials of grafted tomatoes to study yield performance in relation to various rootstock and scion combinations",
  "Lab Techician","Vegetable Breeding Lab, TAMU", "College Station, TX", "May 2017 - Dec 2017", "Screened pepper hybrids for thrip resistance and performed hybrid testing at multiple locations across Texas",
  "Lab Techician", "Vegetable Breeding Lab, TAMU", "College Station, TX", "May 2017 - Dec 2017", "Crossed pepper, tomato, melon and squash to produce hybrid seed",
 "Graduate Research Assistant", "Vegetable Breeding Lab, TAMU", "College Station, TX", "Aug 2014 - Dec 2016", "Measure morphological root traits using the WinRhizo software",
  "Graduate Research Assistant", "Vegetable Breeding Lab, TAMU", "College Station, TX", "Aug 2014 - Dec 2016", "Extracted, purified, and quantified tomato DNA for GBS library",
  "Graduate Research Assistant", "Vegetable Breeding Lab, TAMU", "College Station, TX", "Aug 2014 - Dec 2016", "Constructed linkage map for mapping population using R/qtl, AsMap, and Joinmap",
  "Graduate Research Assistant", "Vegetable Breeding Lab, TAMU", "College Station, TX", "Aug 2014 - Dec 2016", "Mapped 29 QTLs for 12 root and shoot traits using R/qtl, WinQTLCartographer, MapQTL and QTLNetworks",
   "Undergraduate Research Assistant", "Biomass Engineering Lab, CAU", "Beijing, China", "Nov 2012 - Apr 2014", "Reutilized agricultural wastse, e.g. dairy manure and sweetpotato vine, into clean and renewable energy",
  "Undergraduate Research Assistant", "Biomass Engineering Lab, CAU", "Beijing, China", "Nov 2012 - Apr 2014", "Evaluated the volatile fat acid of effluent using HPLC",
  "Undergraduate Research Assistant", "Biomass Engineering Lab, CAU", "Beijing, China", "Nov 2012 - Apr 2014", "Observed dairy manure and sweetpotato vine at a ration of 2:8 could have  as stable methane production"
  )%>%
detailed_entries(positon, dates, uni, loc, details)
```

# Teaching & Mentoring

```{r tutoring}
tribble(
  ~ role, ~ uni, ~ campus, ~ dates, ~ details,
  "Teaching Assistant", "University of Georgia", "Athens, GA", "2019 Fall & 2022 Fall", "Concepts in Biology (BIOL1103), ~70 students; Principles of Plant Biology (PBIO1210), ~ 30 students",
  "Teaching Assistant", "University of Georgia", "Athens, GA", "2019 Fall & 2022 Fall", "Led lab sessions and field trips for students",
   "Teaching Assistant", "University of Georgia", "Athens, GA", "2019 Fall & 2022 Fall", "Hold office hours and graded assigned homework", 
  "Mentor", "University of Georgia", "Athens, GA", "2020-2022", "Sydney Page, CURO Project: Discovery of mirconutrients content of different root architecture types in Common Bean",
  "Mentor", "University of Georgia", "Athens, GA", "2020-2022", "Joslyn Mcklveen, CURO Project: Analysis the effect of temperature and humidity on plant development on a newly-developed mesocosm system",
  "Mentor", "University of Georgia", "Athens, GA", "2020-2022", "Lilly Adams, REU Project: Developing a new image processing pipeline to extract root trait of Arabidopsis and identifying candidate genes for root traits using GWAS",
) %>% 
  detailed_entries(role, dates, uni, campus, details)
```
<!-- \pagebreak -->

# Agricultural Extension
```{r extension}
tribble(
  ~ positon, ~ uni, ~ loc, ~ dates, ~ details,
  "Intern", "Center for Chinese Agricultural Policy (CCAP)", "Beijing, China", "Aug 2011", "Participated the Farmer Field School Promotion Project led by CCAP, Ministry of Agriculture, and Rand Corporation (US)",
   "Intern", "Center for Chinese Agricultural Policy (CCAP)", "Beijing, China", "Aug 2011", "Investigated application of pesticides and fertilizers in tomato productions in Hubei Province",
     "Intern", "Center for Chinese Agricultural Policy (CCAP)", "Beijing, China", "Aug 2011", "Surveyed farmers in three villages and analyzed the questionare data",
  "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Investigated the overuse of additives in the daylily industry in Qidong County",
    "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Surveyed with local farmers and small business owners (>200 people)",
    "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Presented results to the local government and appeared on the local media",
   "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Organized a workshop introducing alternative methods to preserve daylily for farmers ",
  "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Won the Excellent Investigators Team Award ",
  )%>%
detailed_entries(positon, dates, uni, loc, details)
```


# Skills
**Bioinformatics**: NGS (GBS, RNA-Seq), Reads Alignment (Bowtie, GSNAP), SNP Calling (Tophat, VCF Tools, SamTools), Gene Expression Analysis (Cufflinks, Kallisto, Salmon).  

**Quantitative and Population Genetics**: Polygenetic Tree, QTL mapping, Marker Assistant Selection, GWAS.

**Computer and Data Sciences**: Linux/Unix, Python, R, SQL, Github, Docker

**Language Skills**: Chinese (Native), English (Fluent), Japanese (Basic)


# Professional Affiliations 
Member, Crop Science Society of America, Agronomy Society of America, American Society of Agronomy   
Member, North America Plant Phenotyping Network     
Member, American Association for Advancement of Science    
Member, American Society of Horticultural Science      
