---
name: Limeng (Momo) Xie 
date: "`r format(Sys.time(), '%B, %Y')`"
address: Athens, GA, USA
phone: +1 443-691-8965
email: momosan@uga.edu
github: tomatopepper
linkedin: Limeng (Momo) Xie
twitter: happymomosan
headcolor: 414141
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# Education
```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "Phd student in Plant Biology, GPA 3.96", "University of Georgia (UGA)", "Athens, GA", "2018 - Present", "Advisor: Dr. Alexander Bucksch, Computational Plant Science Lab",
  "Master in Horticultural Science, GPA 3.81", "Texas A&M University (TAMU)", "College Station, TX", "2014 - 2016", "Certificate in Applied Statistics",
   "Master in Horticultural Science, GPA 3.81", "Texas A&M University (TAMU)", "College Station, TX", "2014 - 2016", "Thesis: SNP Discovery and Mapping QTLs Associated with Root Traits and Morphological Traits in Tomato",
  "Bachelor in Agronomy, GPA 3.65", "China Agricultural University (CAU)", "Beijing, China", "2009 - 2014", "Thesis: Evaluation of Methane Production in Anaerobic Reactor with Sweet Potato Vine and Dairy Manure",
  "Exchange Student", "Saga University", "Kyushu, Japan", "2011 - 2012", "Major in Plant` Science and Japanese"
) %>%
  detailed_entries(degree, dates, uni, loc, details)
```

# Publications

**Xie, L.**,Burridge,J., Klepp, N., Miller, J., Lynch, J.P., Bucksch, A.,  Phenotypic spectrum: uncovering root architecture diversity in common bean (*Phaseolus vulgaris L.*) *In prep*  

Delory, B.M., Hernandez-Soriano, M.C., Wacker, T.S., Dimitrova, A., Ding, Y., Greeley, L.A., Ng, J.L.P., Mesa-Marín, J., **Xie, L.**, Zheng, C. and York, L.M., 2022. A snapshot of the root phenotyping landscape in 2021. bioRxiv.

**Xie, L.**, Klein, P., Crosby, K., & Jifon, J. (2019). A Genotyping-by-sequencing Single Nucleotide Polymorphism–based Map and Genetic Analysis of Root Traits in an Interspecific Tomato Population, _Journal of the American Society for Horticultural Science_ 144(6), 394-404. 

# Presentations

2022 **Xie, L.,** Burridge,J., Lynch, J.P., Bucksch, A., **North America Plant Phenoytping Network**, _Oral_: "Phenotypic Spectrum: Uncovering Root Architecture Diversity in Common Bean ( _Phaseolus vulgaris_ .L)", Athens, GA

2021 **Xie, L.,** Burridge,J., Lynch, J.P., Bucksch, A., **ASA, CSSA, SSSA International Annual Meeting**, _Poster_: "Phenotypic Spectrum: Uncovering Root Architecture Diversity in Common Bean ( _Phaseolus vulgaris_ .L)", Salt Lake City, UT

2021 Kim, C., **Xie, L.,** Bucksch, A., Seymore, L., Van Iersel, M., **American Society of Horticultural Science Annual Meeting**, _Poster_: "Quantification of Canopy Size Using Automated Chlorophyll Florescence Image Analysis", Denver, CO

2019 **Xie, L.**, Bucksch, A., **International Plant Phenotyping Symposium**, _Poster_: "The shape of plants revealed: A shape theoretic perspective on statistics of trait measurements", Nanjing, China

2019 **Xie, L.**,Burridge,J., Klepp, N., Miller, J., Chutoe, C., Saengwilai, P., Lynch, J.P., Bucksch, A., **Crops Conference**, _Poster_: "The Phenotypic Spectrum: Identifying Whole Role Architecture Types in Genotypes of Common Bean ( _Phaseolus vulgaris_ .L)", Huntsville, AL 

2018 **Xie, L.**, Liu, S, Bucksch., A., **Plant Center Fall Retreat**, _Poster_: "Extracting Traits from 3D Models of Maize Root System Architecture", Unicoi State Park, GA  

2017 **Xie, L.**, Klein, P., Crosby, K., & Jifon, J., **American Society of Horticultural Science Annual Meeting**, _Talk_: "Mapping Novel QTLs Associated with Root Morphological Traits in an Interspecific Tomato Population", Waikoloa, HI  

2015 **Xie, L.**, Crosby, K., & Jifon, J., **American Society of Horticultural Science Annual Meeting**, _Poster_: “Estimates of Genetic Variance for Drought Tolerance Traits in Tomato”, New Orleans, LA 


# Awards
2022 Georgia Education Board Fellowship, UGA      
2022 Gerald O Mott Award, Crop Science Society of America    
2022 Best Fast-Forward Talk at North America Plant Phenotyping Network    
2021 Best Poster Award UGA Phenomics Symposium, UGA      
2021 Georgia Education Board Fellowship     
2020 Palfrey Travel Award, Department of Plant Biology, UGA      
2020 Travel Scholarship for Root Short Course, University of Florida     
2016 Outstanding Graduate Student Award, Texas Plant Protection Association  
2013 Third Prize Scholarship for Academic Excellence, CAU  
2012 Japan Student Service Scholarship, Japan Student Service Organization  
2011 Third Prize Scholarship for Academic Excellence, CAU  
2010 Second Prize Scholarship for Academic Excellence, CAU  
2010 National Scholarship for Encouragement, Ministry of Education in China  
2010 Merit Undergraduate Student Award, CAU 

# Resarch Experience 
```{r research}
tribble(
  ~ positon, ~ uni, ~ loc, ~ dates, ~ details,
  "North America Breeding Intern", "Bayer", "Chesterfield, MO", "2022 May - Present", "Developed a root phenotyping platform for cotton",
  "North America Breeding Intern", "Bayer", "Chesterfield, MO", "2022 May - Present", "Identified root traits that improve cotton performance in drought from control enviroment to field scale",
      "North America Breeding Intern", "Bayer", "Chesterfield, MO", "2022 May - Present", "Presented findings to stakeholders across teams",
  "Graduate Reserch Assistant", "Computational Plant Science Lab, UGA", "Athens, GA", "2018 - Present", "Current project: The phenotypic spectrum: quantifying the diversity of root architecture in common bean",
  "Graduate Reserch Assistant", "Computational Plant Science Lab, UGA", "Athens, GA", "2018 - Present", "Rotation projects: Developed an image processing pipeline to automatically extract root traits from 3D models of maize root system",
   "Graduate Reserch Assistant", "Computational Plant Science Lab, UGA", "Athens, GA", "2018 - Present", "Rotation projects: Identified potential genetic regions with insulators in Bladderwort by analyzing a public RNA-seq database",
  "Graduate Reserch Assistant", "Computational Plant Science Lab, UGA", "Athens, GA", "2018 - Present", "Rotation projects: Explored genetic variation of volatile content among 150 tomato accessions (wild, semi-domesticated, domesticated)",
  "Lab Techician", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2017", "Conducted all daily operations including plant, fertilize, trellis, prune, IPM, supplies and asset acquisition to complete short term and long breeding  goals over 7 greenhouses and acre-size field",
  "Lab Techician", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2017", "Established greenhouse trials of grafted tomatoes to study yield performance in relation to various rootstock and scion combinations",
  "Lab Techician","Vegetable Breeding Lab, TAMU", "College Station, TX", "2017", "Screened pepper hybrids for thrip resistance and performed hybrid testing at multiple locations across Texas",
  "Lab Techician", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2017", "Crossed pepper, tomato, melon and squash to produce hybrid seed",
 "Graduate Research Assistant", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2014-2016", "Measure morphological root traits using the WinRhizo software",
  "Graduate Research Assistant", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2014-2016", "Extracted, purified, and quantified tomato DNA for GBS library",
  "Graduate Research Assistant", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2014-2016", "Constructed linkage map for mapping population using R/qtl, AsMap, and Joinmap",
  "Graduate Research Assistant", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2014-2016", "Mapped 29 QTLs for 12 root and shoot traits using R/qtl, WinQTLCartographer, MapQTL and QTLNetworks",
   "Undergraduate Research Assistant", "Biomass Engineering Lab, CAU", "Beijing, China", "2012-2014", "Reutilized agricultural wastse, e.g. dairy manure and sweetpotato vine, into clean and renewable energy",
  "Undergraduate Research Assistant", "Biomass Engineering Lab, CAU", "Beijing, China", "2012-2014", "Evaluated the volatile fat acid of effluent using HPLC",
  "Undergraduate Research Assistant", "Biomass Engineering Lab, CAU", "Beijing, China", "2012-2014", "Observed dairy manure and sweetpotato vine at a ration of 2:8 could have  as stable methane production"
  )%>%
detailed_entries(positon, dates, uni, loc, details)
```

# Teaching & Mentoring

```{r tutoring}
tribble(
  ~ role, ~ uni, ~ campus, ~ dates, ~ details,
  "Teaching Assistant", "University of Georgia", "Athens, GA", "2019 Fall", "Concepts in Biology (BIOL1103), ~70 students",
  "Teaching Assistant", "University of Georgia", "Athens, GA", "2019 Fall", "Presented lectures for 3 lab session during semester",
   "Teaching Assistant", "University of Georgia", "Athens, GA", "2019 Fall", "Lead field trip and graded assigned homework for class",
   "Teaching Assistant", "University of Georgia", "Athens, GA", "2019 Fall", "Achieved overall student approval rating of 4.38 on 5 point scale",
  "Mentor", "University of Georgia", "Athens, GA", "2020-2022", "Sydney Page, CURO Project: Discovery of mirconutrients content of different root architecture types in Common Bean",
  "Mentor", "University of Georgia", "Athens, GA", "2020-2022", "Joslyn Mcklveen, CURO Project: Analysis the effect of temperature and humidity on plant development on a newly-developed mesocosm system",
  "Mentor", "University of Georgia", "Athens, GA", "2020-2022", "Lilly Adams, REU Project: Developing a new image processing pipeline to extract root trait of Arabidopsis and identifying candidate genes for root traits from GWAS",
  "Mentor", "Texas A&M University", "College Station, TX", "May 2017 - Dec 2017", "Trained 8 undergraduates for pepper and tomato breeding"
) %>% 
  detailed_entries(role, dates, uni, campus, details)
```
<!-- \pagebreak -->

# Agricultural Extension
```{r extension}
tribble(
  ~ positon, ~ uni, ~ loc, ~ dates, ~ details,
  "Intern", "Center for Chinese Agricultural Policy (CCAP)", "Beijing, China", "Aug 2011", "Participated the Farmer Field School Promotion Project led by CCAP, Ministry of Agriculture, and Rand Corporation (US)",
   "Intern", "Center for Chinese Agricultural Policy (CCAP)", "Beijing, China", "Aug 2011", "Investigated application of pesticides and fertilizers in tomato productions in Hubei Province",
     "Intern", "Center for Chinese Agricultural Policy (CCAP)", "Beijing, China", "Aug 2011", "Surveyed farmers in three villages and analyzed the questionare data",
  "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Investigated the overuse of additives in the daylily industry in Qidong County",
    "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Surveyed with local farmers and small business owners (>200 people)",
    "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Presented results to the local government and appeared on the local media",
   "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Organized a workshop introducing alternative methods to preserve daylily for farmers ",
  "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Won the Excellent Investigators Team Award ",
  )%>%
detailed_entries(positon, dates, uni, loc, details)
```

# Leadership Acctivities

2021 Ambassador of International Society of Root Research | Responsible for promoting and advocating root re‐ search at the social media platform  
2021 Panelist Speaker of Women in STEM for Outreach Activities in Athens‐Clarke County High School  
2021 Judge for Senior Section of 73rd Georgia Science & Engineering Fair  
2020 Judge Lead for Junior Section of 72nd Georgia Science & Engineering Fair  
2019 Judge for Senior Section of 71st Georgia Science & Engineering Fair  
2019 Executive Board Member of Chinese Genomics Online Meet‐up | Responsible for inviting guest speakers and technical support for live stream  
2018 Volunteer in March for Science at Washington, DC  
2015 Secretary, Texas A&M Horticulture Graduate Student Council  
2015 Volunteer, Texas A&M Plant Breeding Symposium  


# Professional Affiliations 
Member, Crop Science Society of America, Agronomy Society of America, American Society of Agronomy   
Member, North America Plant Phenotyping Network     
Member, American Association for Advancement of Science    
Member, American Society of Horticultural Science      

# Skills
**Bioinformatics**: NGS (GBS, RNA-Seq), Reads Alignment (Bowtie, GSNAP), SNP Calling (Tophat, VCF Tools, SamTools), Gene Expression Analysis (Cufflinks)  
**Quantitative and Population Genetics**: Polygenetic Tree, QTL mapping, Marker Assistant Selection, Clustering, Principle Component Analysis  
**Computer and Data Sciences**: Linux/Unix, Python (Pandas, Numpy, OpenCV, Sci-py, Jupyter Notebooks), R (R/qtl, ggplot2, Rmarkdown, Tidyverse), SQL (MariaDB, Dbeaver), Github  
**Language Skills**: Chinese (Native), English (Fluent), Japanese (Basic)