---
name: Limeng (Momo) Xie 
date: "`r format(Sys.time(), '%B, %Y')`"
address: 108 College Station Rd, Apt H204, Athens, GA, USA, 30605
phone: +1 443-691-8965
email: momosan@uga.edu
github: tomatopepper
linkedin: Limeng (Momo) Xie
twitter: happymomosan
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# Education
```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "Phd Candidate in Plant Biology, GPA 3.96", "University of Georgia (UGA)", "Athens, GA", "2018 - Present", "Advisor: Dr. Alexander Bucksch, Computational Plant Science Lab",
  "Master in Horticultural Science, GPA 3.81", "Texas A&M University (TAMU)", "College Station, TX", "2014 - 2016", "Certificate in Applied Statistics",
   "Master in Horticultural Science, GPA 3.81", "Texas A&M University (TAMU)", "College Station, TX", "2014 - 2016","Advisors: Dr. John Jifon & Dr. Kevin Crosby",
   "Master in Horticultural Science, GPA 3.81", "Texas A&M University (TAMU)", "College Station, TX", "2014 - 2016", "Thesis: SNP Discovery and Mapping QTLs Associated with Root Traits and Morphological Traits in Tomato",
  "Bachelor in Agronomy, GPA 3.65", "China Agricultural University (CAU)", "Beijing, China", "2009 - 2014", "Thesis: Evaluation of Methane Production in Anaerobic Reactor with Sweet Potato Vine and Dairy Manure",
  "Exchange Student", "Saga University", "Kyushu, Japan", "2011 - 2012", "Major in Plant Science and Japanese"
) %>%
  detailed_entries(degree, dates, uni, loc, details)
```

# Research Experience  
```{r research}
tribble(
  ~ positon, ~ uni, ~ loc, ~ dates, ~ details,
  "Graduate Reserch Assistant", "Computational Plant Science Lab, UGA", "Athens, GA", "2018 - Present", "Current project: Design and excute computational pipelines and greenhouse experiments to uncover the causes of root architecture diversity in common bean",
  "Graduate Reserch Assistant", "Computational Plant Science Lab, UGA", "Athens, GA", "2018 - Present", "Rotation projects: 1. Developed an image processing pipeline to automatically extract root traits from 3D models of maize root system; 2. Identified potential genetic regions with insulators in Bladderwort by analyzing a public RNA-seq database; 3. Explored genetic variation of volatile content among 150 tomato accessions (wild, semi-domesticated, domesticated)",
  #  "Graduate Reserch Assistant", "Computational Plant Science Lab, UGA", "Athens, GA", "2018 - Present", " Identified potential genetic regions with insulators in Bladderwort by analyzing a public RNA-sea database",
  # "Graduate Reserch Assistant", "Computational Plant Science Lab, UGA", "Athens, GA", "2018 - Present", "Rotation projects: Explored genetic variation of volatile content among 150 tomato accessions (wild, semi-domesticated, domesticated).",
  "Lab Techician", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2017", "Conducted all daily operations including planting, fertilize, trellis, prune, IPM, supplies and asset acquisition to complete short and long breeding term goals over 7 greenhouses and acre-size field",
  "Lab Techician", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2017", "Established greenhouse trials of grafted tomatoes to study yield performance in relation to various rootstock and scion combinations",
  "Lab Techician","Vegetable Breeding Lab, TAMU", "College Station, TX", "2017", "Screened pepper hybrids for thrip resistance and performed hybrid testing at multiple locations across Texas",
  "Lab Techician", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2017", "Crossed pepper, tomato, melon and squash to produce hybrid seed",
 "Graduate Research Assistant", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2014-2016", "Measured morphological root traits using the WinRhizo software",
  "Graduate Research Assistant", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2014-2016", "Extracted, purified, and quantified tomato DNA for GBS library",
  "Graduate Research Assistant", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2014-2016", "Constructed a linkage map for mapping population using R/qtl, AsMap, and Joinmap",
  "Graduate Research Assistant", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2014-2016", "Mapped 29 QTLs for 12 root and shoot traits using R/qtl, WinQTLCartographer, MapQTL and QTLNetworks",
   "Undergraduate Research Assistant", "Biomass Engineering Lab, CAU", "Beijing, China", "2012-2014", "Reutilized agricultural wastse, e.g. dairy manure and sweetpotato vine, into clean and renewable energy",
  "Undergraduate Research Assistant", "Biomass Engineering Lab, CAU", "Beijing, China", "2012-2014", "Evaluated the volatile fat acid of effluent using HPLC",
  "Undergraduate Research Assistant", "Biomass Engineering Lab, CAU", "Beijing, China", "2012-2014", "Obtained a opitmal ratio of dairy manure and sweetpotato vine (2:8) to achieve the stable methane production"
  )%>%
detailed_entries(positon, dates, uni, loc, details)
```
\pagebreak

# Teaching & Mentoring

```{r tutoring}
tribble(
  ~ role, ~ uni, ~ campus, ~ dates, ~ details,
  "Teaching Assistant", "University of Georgia", "Athens, GA", "Aug 2019 - Dec 2019", "Concepts in Biology (BIOL1103), ~70 students",
  "Teaching Assistant", "University of Georgia", "Athens, GA", "Aug 2019 - Dec 2019", "Presented lectures for 3 lab session during semester",
   "Teaching Assistant", "University of Georgia", "Athens, GA", "Aug 2019 - Dec 2019", "Led field trip and graded assigned homework for class",
   "Teaching Assistant", "University of Georgia", "Athens, GA", "Aug 2019 - Dec 2019", "Achieved overall student approval rating of 4.38 on 5 point scale",
  "Mentor", "University of Georgia", "Athens, GA", "May 2020 - Present", "Sydney Page, Research Project: Investigating how different water levels affect root-shoot allocation across various developmental stages and genotypes in common bean (2021 Summer-Fall)",
  "Mentor", "University of Georgia", "Athens, GA", "May 2020 - Present", "Lilly Adams, REU Project: Developing a new image processing pipeline to extract root trait of Arabidopsis and identifying candidate genes for root traits from GWAS (2020 Summer); Best Poster Prize at 2021 INSPIRE LSAMP Annual Conference",
  "Mentor", "University of Georgia", "Athens, GA", "May 2020 - Present", "Joslyn Mcklveen, CURO Project: Understanding Environmental Parameters' Effects on Common Bean Micronutrient Content (2020 Summer-Fall & 2021 Spring)",
  "Mentor", "Texas A&M University", "College Station, TX", "May 2017 - Dec 2017", "Trained a team of 8 undergraduates in the pepper and tomato breeding program"
) %>% 
  detailed_entries(role, dates, uni, campus, details)
```

# Agricultural Extension 
```{r extension}
tribble(
  ~ positon, ~ uni, ~ loc, ~ dates, ~ details,
  "Intern", "Center for Chinese Agricultural Policy (CCAP)", "Beijing, China", "Aug 2011", "Participated the Farmer Field School Promotion Project led by CCAP, Ministry of Agriculture, and Rand Corporation (US)",
  "Intern", "Center for Chinese Agricultural Policy (CCAP)", "Beijing, China", "Aug 2011", "Investigated application of pesticides and fertilizers in tomato productions in Hubei Province",
  "Intern", "Center for Chinese Agricultural Policy (CCAP)", "Beijing, China", "Aug 2011", "Surveyed farmers in three villages and analyzed the questionare data",
  "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Investigated the overuse of additives in the daylily industry in Qidong County",
    "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Surveyed with local farmers and small business owners (>200 people)",
    "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Presented results to the local government and appeared on the local media",
   "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Organized a workshop introducing alternative methods to preserve daylily for farmers ",
  "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Won the Excellent Investigators Team Award ",
  )%>%
detailed_entries(positon, dates, uni, loc, details)
```

# Publications
**Xie, L.**,Burridge,J., Klepp, N., Miller, J., Lynch, J.P., Bucksch, A.,  Phenotypic spectrum: uncovering root architecture diversity in common bean (*Phaseolus vulgaris L.*). *In prep*  

**Xie, L.**, Klein, P., Crosby, K., & Jifon, J. (2019). A Genotyping-by-sequencing Single Nucleotide Polymorphism Map and Genetic Analysis of Root Traits in an Interspecific Tomato Population, _Journal of the American Society for Horticultural Science_ 144(6), 394-404. 


 
# Presentations

2021 **Xie, L.**,Burridge,J., Lynch, J.P., Bucksch, A., **ASA, CSSA, SSSA International Annual Meeting**,  _Oral_: Phenotypic Spectrum: Uncovering Root Architecture Diversity in Common Bean ( _Phaseolus vulgaris_ .L), Salt Lake City, UT

2021 Kim, C., **Xie, L.**, Bucksch, A., Seymore, L., Van Iersel, M., **American Society of Horticultural Science Annual Meeting**, _Poster_:Quantification of Canopy Size Using Automated Chlorophyll Florescence Image Analysis, Denver, CO

2021 **Xie, L.**,Burridge,J., Lynch, J.P., Bucksch, A., **North American Plant Phenotyping Network Annual Conference**,  _Poster_: Phenotypic Spectrum: Uncovering Root Architecture Diversity in Common Bean ( _Phaseolus vulgaris_ .L), Online

2020 **Xie, L.**,Burridge,J., Klepp, N., Miller, J.,Lynch, J.P., Bucksch, A., **the 7th International Horticulture Research Conference**,  _Poster_: Quantifying diversity of root architecture types within a genotype of common bean ( _Phaseolus vulgaris_ .L), Online  

2019 **Xie, L.**, Bucksch, A., **International Plant Phenotyping Symposium**, _Poster_: The shape of plants revealed: A shape theoretic perspective on statistics of trait measurements, Nanjing, China

2019 **Xie, L.**,Burridge,J., Klepp, N., Miller, J., Chutoe, C., Saengwilai, P., Lynch, J.P., Bucksch, A., **Crops Conference**, _Poster_:The Phenotypic Spectrum: Identifying Whole Role Architecture Types in Genotypes of Common Bean ( _Phaseolus vulgaris_ .L), Huntsville, AL 

2018 **Xie, L.**, Liu, S, Bucksch., A., **Plant Center Fall Retreat**, _Poster_: Extracting Traits from 3D Models of Maize Root System Architecture", Unicoi State Park, GA  

2017 **Xie, L.**, Klein, P., Crosby, K., & Jifon, J., **American Society of Horticultural Science Annual Meeting**, _Oral_: Mapping Novel QTLs Associated with Root Morphological Traits in an Interspecific Tomato Population, Waikoloa, HI  


<!-- 2016 **Xie, L.**, Klein, P., Crosby, K., & Jifon, J., **Annual Meeting of Texas Plant Protection Association**, _Poster_: SNP Discovery and QTL Mapping for Root Related Traits in an Interspecific Tomato Population, Bryan, TX -->

<!-- 2015 **Xie, L.**, Crosby, K., & Jifon, J.,**Annual Meeting of Texas Plant Protection Association**, _Poster_: Estimates of Genetic Variance for Drought Tolerance Traits in Tomato, Bryan, TX  -->

2015 **Xie, L.**, Crosby, K., & Jifon, J., **American Society of Horticultural Science Annual Meeting**, _Poster_: Estimates of Genetic Variance for Drought Tolerance Traits in Tomato, New Orleans, LA 


# Awards
2021 Best Poster Award UGA Phenomics Symposium, UGA   
2021 Graduate Education Advancement Graduate Fellowship, Graduate School, UGA   
2020 Palfrey Travel Award, Department of Plant Biology, UGA  
2020 Travel Scholarship for Root Short Course, University of Florida  
2016 Outstanding Graduate Student Award, Texas Plant Protection Association  
2013 Third Prize Scholarship for Academic Excellence, CAU  
2012 Japan Student Service Scholarship, Japan Student Service Organization  
2011 Third Prize Scholarship for Academic Excellence, CAU  
2010 Second Prize Scholarship for Academic Excellence, CAU  
2010 National Scholarship for Encouragement, Ministry of Education in China  
2010 Merit Undergraduate Student Award, CAU 

# Leadership and Community Service
2021   Encompass Scholar of ASA, CSSA, SSSA to connect under-represented STEM students, sciecne and mentorship    
2021   Ambassador of International Society of Root Research | Responsible for promoting and advocating root research at the social media platform    
2021   Panelist Speaker of Women in STEM for Outreach Activities in Athens-Clarke County High School   
2021   Judge for Senior Section of 73rd Georgia Science & Engineering Fair    
2020   Judge Lead for Junior Section of 72nd Georgia Science & Engineering Fair  
2019   Judge for Senior Section of 71st Georgia Science & Engineering Fair  
2019   Executive Board Member of Chinese Genomics Online Meet-up | Responsible for inviting guest speakers and technical support for live stream    
2018   Volunteer in March for Science at Washington, DC      
2015   Secretary, Texas A&M Horticulture Graduate Student Council  
2015   Volunteer, Texas A&M Plant Breeding Symposium  
2012   Speaker, Introduction of Chinese culture to students at local elementary schools in Ichikikushikino-shi, kagoshima, Japan  
2011   CAU Ambassador, Student representative for university-wide foreign affair activities, CAU  
2010   Scrum Half Player of College Rugby Team | Won the champion of college wide games, CAU  
2010   Volunteer, Helped take care of senior people monthly at a Elder Care Center, Beijing  
2009   Tutor for a group of middle school students and several high school students in science courses, Qimen & Beijing  

# Professional Affiliations 
Member, Botanical Society of America  
Member, American Association for Advancement of Science  
Member, Phi Alpha Xi Honor Society  
Member, American Society of Horticultural Science   
Member, Crop science Society of America   
Member, Graduate Women in Science  

# Skills
**Bioinformatics**: NGS (GBS, RNA-Seq), Reads Alignment (Bowtie, GSNAP), SNP Calling (Tophat, VCF Tools, SamTools), Gene Expression Analysis (Cufflinks, Kallisto)  
**Quantitative and Population Genetics**: Polygenetic Tree, QTL mapping, Marker Assistant Selection, GWAS
**Computer and Data Sciences**: Linux/Unix, Python (Pandas, Numpy, OpenCV, Sci-py, Jupyter Notebooks), R (R/qtl, ggplot2, Rmarkdown, Tidyverse), SQL (MariaDB, Dbeaver), Github  
**Language Skills**: Chinese (Native), English (Fluent), Japanese (Basic)