---
name: Limeng (Momo) Xie 
date: "`r format(Sys.time(), '%B, %Y')`"
address: Athens, GA, USA
phone: +1 443-691-8965
email: momosan@uga.edu
github: tomatopepper
linkedin: Limeng (Momo) Xie
twitter: happymomosan
headcolor: 414141
output: 
  vitae::awesomecv:
    keep_tex: true
    format: word 
---

```{r setup, include=FALSE}
library(dplyr)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# Education
```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "Phd student in Plant Biology, GPA 4.00", "University of Georgia (UGA)", "Athens, GA", "2018 - Present", "Advisor: Dr. Alexander Bucksch, Computational Plant Science Lab",
  "Master in Horticultural Science, GPA 3.81", "Texas A&M University (TAMU)", "College Station, TX", "2014 - 2016", "Certificate in Applied Statistics",
   "Master in Horticultural Science, GPA 3.81", "Texas A&M University (TAMU)", "College Station, TX", "2014 - 2016","Advisors: Dr.Kevin Crosby & Dr.John Jifon, Vegetable Breeding Lab",
   "Master in Horticultural Science, GPA 3.81", "Texas A&M University (TAMU)", "College Station, TX", "2014 - 2016", "Thesis: SNP Discovery and Mapping QTLs Associated with Root Traits and Morphological Traits in Tomato",
  "Bachelor in Agronomy, GPA 3.65", "China Agricultural University (CAU)", "Beijing, China", "2009 - 2014", "Thesis: Evaluation of Methane Production in Anaerobic Reactor with Sweet Potato Vine and Dairy Manure",
  "Exchange Student", "Saga University", "Kyushu, Japan", "2011 - 2012", "Major in Plant` Science and Japanese"
) %>%
  detailed_entries(degree, dates, uni, loc, details)
```

# Publications

**Xie, L.**,Burridge,J., Klepp, N., Miller, J., Lynch, J.P., Bucksch, A.,  Phenotypic spectrum: uncovering root architecture diversity in common bean (*Phaseolus vulgaris L.*) *In prep* 

Delory, B.M., Hernandez-Soriano, M.C., Wacker, T.S., Dimitrova, A., Ding, Y., Greeley, L.A., Ng, J.L.P., Mesa-Marín, J., **Xie, L.**, Zheng, C. and York, L.M., (2022). A snapshot of the root phenotyping landscape in 2021. bioRxiv. (Submitted to New Phytologist, under revision)

**Xie, L.**, Klein, P., Crosby, K., & Jifon, J. (2019). A Genotyping-by-sequencing Single Nucleotide Polymorphism Map and Genetic Analysis of Root Traits in an Interspecific Tomato Population, _Journal of the American Society for Horticultural Science_ 144(6), 394-404. 


 
# Presentations

2022 Xie, L.,Burridge,J., Lynch, J.P., Bucksch, A., **North American Plant Phenotyping Network Annual Conference**, _Oral_: Phenotypic Spectrum: Uncovering Root Architecture Diversity in Common Bean ( _Phaseolus vulgaris_ .L), Athens, GA    

2021 **Xie, L.**,Burridge,J., Lynch, J.P., Bucksch, A., **ASA, CSSA, SSSA International Annual Meeting**,  _Oral_: Phenotypic Spectrum: Uncovering Root Architecture Diversity in Common Bean ( _Phaseolus vulgaris_ .L), Salt Lake City, UT

2021 Kim, C., **Xie, L.**, Bucksch, A., Seymore, L., Van Iersel, M., **American Society of Horticultural Science Annual Meeting**, _Poster_:Quantification of Canopy Size Using Automated Chlorophyll Florescence Image Analysis, Denver, CO

2021 **Xie, L.**,Burridge,J., Lynch, J.P., Bucksch, A., **North American Plant Phenotyping Network Annual Conference**,  _Poster_: Phenotypic Spectrum: Uncovering Root Architecture Diversity in Common Bean ( _Phaseolus vulgaris_ .L), Online

2020 Xie, L., Burridge,J., Klepp, N., Miller, J.,Lynch, J.P., Bucksch, A.,  **9th International Conference on FUNCTIONAL-STRUCTURAL PLANT MODELS, FSPM Towards Computable Plants**, _Poster_: Phenotypic spectrum: quantifying diversity of root architectures within genotypes on the example common bean ( _Phaseolus vulgaris_ .L), Online

2020 **Xie, L.**,Burridge,J., Klepp, N., Miller, J.,Lynch, J.P., Bucksch, A., **the 7th International Horticulture Research Conference**,  _Poster_: Quantifying diversity of root architecture types within a genotype of common bean ( _Phaseolus vulgaris_ .L), Online  

2019 **Xie, L.**, Bucksch, A., **International Plant Phenotyping Symposium**, _Poster_: The shape of plants revealed: A shape theoretic perspective on statistics of trait measurements, Nanjing, China

2019 **Xie, L.**,Burridge,J., Klepp, N., Miller, J., Chutoe, C., Saengwilai, P., Lynch, J.P., Bucksch, A., **Crops Conference**, _Poster_:The Phenotypic Spectrum: Identifying Whole Role Architecture Types in Genotypes of Common Bean ( _Phaseolus vulgaris_ .L), Huntsville, AL 

2018 **Xie, L.**, Liu, S, Bucksch., A., **Plant Center Fall Retreat**, _Poster_: Extracting Traits from 3D Models of Maize Root System Architecture", Unicoi State Park, GA  

2017 **Xie, L.**, Klein, P., Crosby, K., & Jifon, J., **American Society of Horticultural Science Annual Meeting**, _Talk_: "Mapping Novel QTLs Associated with Root Morphological Traits in an Interspecific Tomato Population, Waikoloa, HI  

2015 **Xie, L.**, Crosby, K., & Jifon, J., **American Society of Horticultural Science Annual Meeting**, _Poster_: Estimates of Genetic Variance for Drought Tolerance Traits in Tomato, New Orleans, LA 


# Honors and Awards
2022 Best Fast-Forward Talk Award at North American Plant Phenotyping Network Annual Conference
2022 Gerald O. Mott Award, Crop Science Society of America
2021 Best Poster Award at Phenomics and Plant Robotics Center Symposium, UGA
2021 Graduate Education Advancement Graduate Fellowship, Graduate School, UGA
2020 Palfrey Travel Award, Department of Plant Biology, UGA  
2020 Travel Scholarship for Root Short Course, University of Florida  
2016 Outstanding Graduate Student Award, Texas Plant Protection Association  
2013 Third Prize Scholarship for Academic Excellence, CAU  
2012 Japan Student Service Scholarship, Japan Student Service Organization  
2011 Third Prize Scholarship for Academic Excellence, CAU  
2010 Second Prize Scholarship for Academic Excellenc, CAU  
2010 National Scholarship for Encouragement, Ministry of Education in China  
2010 Honor Undergrate Student Award, CAU 

# Research Experience 
```{r research}
tribble(
  ~ positon, ~ uni, ~ loc, ~ dates, ~ details,
  "Graduate Reserch Assistant", "Computational Plant Science Lab, UGA", "Athens, GA", "2018 - Present", "Current project: The phenotypic spectrum: quantifying the diversity of root architecture in common bean",
  "Graduate Reserch Assistant", "Computational Plant Science Lab, UGA", "Athens, GA", "2018 - Present", "Rotation projects: Developed an image processing pipeline to automatically extract root traits from 3D models of maize root system",
   "Graduate Reserch Assistant", "Computational Plant Science Lab, UGA", "Athens, GA", "2018 - Present", "Rotation projects: Identified potential genetic regions with insulators in Bladderwort by analyzing a public RNA-sea database",
  "Graduate Reserch Assistant", "Computational Plant Science Lab, UGA", "Athens, GA", "2018 - Present", "Rotation projects: Explored genetic variation of volatile content among 150 tomato accessions (wild, semi-domesticated, domesticated).",
  "Lab Techician", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2017", "Conducted all daily operations including plant, fertilize, trellis, prune, IPM, supplies and asset acquisition to complete short term and long breeding  goals over 7 greenhouses and acre-size field",
  "Lab Techician", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2017", "Established greenhouse trials of grafted tomatoes to study yield performance in relation to various rootstock and scion combinations",
  "Lab Techician","Vegetable Breeding Lab, TAMU", "College Station, TX", "2017", "Screened pepper hybrids for thrip resistance and performed hybrid testing at multiple locations across Texas",
  "Lab Techician", "Vegetable Breeding Lab, TAMU", "College Station, TX", "2017", "Crossed pepper, tomato, melon and squash to produce hybrid seed.",
  )%>%
detailed_entries(positon, dates, uni, loc, details)
```

# Teaching & Mentoring

```{r tutoring}
tribble(
  ~ role, ~ uni, ~ campus, ~ dates, ~ details,
  "Teaching Assistant", "University of Georgia", "Athens, GA", "2019 Fall", "Concepts in Biology (BIOL1103), ~70 students",
  "Teaching Assistant", "University of Georgia", "Athens, GA", "2019 Fall", "Presented lectures for 3 lab session during semester",
   "Teaching Assistant", "University of Georgia", "Athens, GA", "2019 Fall", "Lead field trip and graded assigned homework for class",
   "Teaching Assistant", "University of Georgia", "Athens, GA", "2019 Fall", "Achieved overall student approval rating of 4.38 on 5 point scale",
  "Mentor", "University of Georgia", "Athens, GA", "2020 Summer", "Lilly Adams, REU Project: Developing a new image processing pipeline to extract root trait of Arabidopsis and identifying candidate genes for root traits from GWAS",
  "Mentor", "University of Georgia", "Athens, GA", "2020 Summer", "Joslyn Mcklveen, CURO Project: Analyze the effect of temperature and humidity on plant development on a newly-developed mesocosm system",
  "Mentor", "Texas A&M University", "College Station, TX", "May 2017 - Dec 2017", "Trained 8 undergraduates of pepper and tomato breeding"
) %>% 
  detailed_entries(role, dates, uni, campus, details)
```
<!-- \pagebreak -->

<!-- # Agricultural Extension -->
<!-- ```{r extension} -->
<!-- tribble( -->
<!--   ~ positon, ~ uni, ~ loc, ~ dates, ~ details, -->
<!--   "Intern", "Center for Chinese Agricultural Policy (CCAP)", "Beijing, China", "Aug 2011", "Participated the Farmer Field School Promotion Project led by CCAP, Ministry of Agriculture, and Rand Corporation (US)", -->
<!--    "Intern", "Center for Chinese Agricultural Policy (CCAP)", "Beijing, China", "Aug 2011", "Investigated application of pesticides and fertilizers in tomato productions in Hubei Province", -->
<!--      "Intern", "Center for Chinese Agricultural Policy (CCAP)", "Beijing, China", "Aug 2011", "Surveyed farmers in three villages and analyzed the questionare data", -->
<!--   "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Investigated the overuse of additives in the daylily industry in Qidong County", -->
<!--     "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Surveyed with local farmers and small business owners (>200 people)", -->
<!--     "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Presented results to the local government and appeared on the local media", -->
<!--    "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Organized a workshop introducing alternative methods to preserve daylily for farmers ", -->
<!--   "Co-leader, Summer Field Program", "China Agricultural University", "Beijing, China", "June 2011", "Won the Excellent Investigators Team Award ", -->
<!--   )%>% -->
<!-- detailed_entries(positon, dates, uni, loc, details) -->
<!-- ``` -->

# Synergistic Activities
2020   Judge Lead for Junior Section of 72nd Georgia Science & Engineering Fair  
2019   Judge for Senior Section of 72nd Georgia Science & Engineering Fair  
2019   Executive Board Member of Chinese Genomics Online Meet-up | Responsible for inviting guest speakers and technical support for live stream 2018   Volunteer for March for Science at Washington, DC  
2015   Secretary, Texas A&M Horticulture Graduate Student Council  
2015   Volunteer, Texas A&M Plant Breeding Symposium  
2012   Spearker, Introduction of Chinese Culture with local schools in Ichikikushikino-shi, kagoshima, Japan  
2011   CAU Ambassador, Student representative for university-wide foreign affair activities, CAU  
2010   Scrum Half Player of College Rugby Team | Won the plateclass champion of college wide games, CAU  

<!-- # Professional Affiliations  -->
<!-- Member, Botanical Society of America   -->
<!-- Member, American Association for Advancement of Science   -->
<!-- Member, Phi Alpha Xi Honor Society   -->
<!-- Member, American Society of Horticultural Science    -->

<!-- # Skills -->
<!-- **Bioinformatics**: NGS (GBS, RNA-Seq), Reads Alignment (Bowtie, GSNAP), SNP Calling (Tophat, VCF Tools, SamTools), Gene Expression Analysis (Cufflinks)   -->
<!-- **Quantitative and Population Genetics**: Polygenetic Tree, QTL mapping, Marker Assistant Selection, Clustering, Principle Component Analysis   -->
<!-- **Computer and Data Sciences**: Linux/Unix, Python (Pandas, Numpy, OpenCV, Sci-py, Jupyter Notebooks), R (R/qtl, ggplot2, Rmarkdown, Tidyverse), SQL (MariaDB, Dbeaver), Github   -->
<!-- **Language Skills**: Chinese (Native), English (Fluent), Japanese (Basic) -->